Reopt

### 2023-04-26 src/reopt_api.Rmd
created function to use list of zipcodes and collect utility data from OpenEI website api

```{r}
## open EI api
openEI_api_key <- "rU6MEqhK9OJ7obAnmcbzYhpFOenfBM5Q8GF0yJFA"

openEI_start <- "https://api.openei.org/utility_rates?version=latest&format=json&sector=Residential&detail=full&approved=true&address=26900&"
# Set the URL for the job submission endpoint

openEI_url <- paste0(openEI_start, "api_key=", openEI_api_key)

EIresponse <- GET(openEI_url)
content <- content(EIresponse, "text")
json <- fromJSON(content)

EIoutput_df <- data.frame(
  label = json$items$label,
  utility = json$items$utility,
  approved = json$items$approved,
  rate_name = json$items$name)

  # extract utility rate information
rates <- json$items$rate
  # print utility rate information for the city
  cat(city, "utility rates:\n")
  for (rate in rates) {
    cat("  - Name:", rate$name, "\n")
    cat("    Description:", rate$description, "\n")
    cat("    Value:", rate$value, "\n")

if (http_type(response)$status_code == 200) {
  data <- fromJSON(content(EIresponse, "text"), simplifyDataFrame = TRUE)

  # Extract relevant information from the data
  utility_name <- data$items[[1]]$utility_name
  utility_type <- data$items[[1]]$sector
  rate_name <- data$items[[1]]$name
  start_date <- data$items[[1]]$start_date
  end_date <- data$items[[1]]$end_date
  rate_structure <- data$items[[1]]$rate_structure
  energy_rate <- data$items[[1]]$rate
  demand_rate <- data$items[[1]]$demand_rate

  # Print the results
  cat(sprintf("Utility name: %s\n", utility_name))
  cat(sprintf("Utility type: %s\n", utility_type))
  cat(sprintf("Rate name: %s\n", rate_name))
  cat(sprintf("Start date: %s\n", start_date))
  cat(sprintf("End date: %s\n", end_date))
  cat(sprintf("Rate structure: %s\n", rate_structure))
  cat(sprintf("Energy rate: %s\n", energy_rate))
  cat(sprintf("Demand rate: %s\n", demand_rate))
} else {
  cat(sprintf("Failed to retrieve data (status code %s)", http_type(response)$status_code))
}

@@

# list of cities
cities <- c("San Francisco", "Los Angeles", "New York")

# loop through each city and get utility rate information
for (city in cities) {
  # construct URL with city name as parameter
  url <- paste0("https://api.openei.org/utility_rates?version=3&format=json&address=", gsub(" ", "+", city))
  # make API call
  response <- GET(url)
  # extract content and parse as JSON
  content <- content(response, "text")
  json <- fromJSON(content)
  # extract utility rate information
  rates <- json$items$rate
  # print utility rate information for the city
  cat(city, "utility rates:\n")
  for (rate in rates) {
    cat("  - Name:", rate$name, "\n")
    cat("    Description:", rate$description, "\n")
    cat("    Value:", rate$value, "\n")
  }
}
```

>>>>

```{r}
```

## open EI api
## open EI api
openEI_api_key <- "rU6MEqhK9OJ7obAnmcbzYhpFOenfBM5Q8GF0yJFA"

openEI_start <- "https://api.openei.org/utility_rates?version=latest&format=json&sector=Residential&detail=full&approved=true&"
# Set the URL for the job submission endpoint

openEI_url <- paste0(openEI_start, "address=", zipcodes, "&api_key=", openEI_api_key)
EIresponse <- GET(openEI_url)
content <- content(EIresponse, "text")
json <- fromJSON(content)

 # extract utility rate information
EIutility_df <- list(
  label = json$items$label,
  utility = json$items$utility,
  rate_name = json$items$name)
```

openEI_start_url <- "https://api.openei.org/utility_rates?version=latest&format=json&sector=Residential&detail=full&approved=true&address="
openEI_api_end <- "&api_key=rU6MEqhK9OJ7obAnmcbzYhpFOenfBM5Q8GF0yJFA"

### Function w for loop
get_utility_data <- function(zipcodes) {
  # Create an empty list to store the resulting data frames
  utility_info <- list()
  # get data for each zipcode in vector
  for (zipcode in zipcodes) {
    openEI_start_url <- "https://api.openei.org/utility_rates?version=latest&format=json&sector=Residential&detail=full&approved=true&address="
    openEI_api_end <- "&api_key=rU6MEqhK9OJ7obAnmcbzYhpFOenfBM5Q8GF0yJFA"

    openEI_url <- paste0(openEI_start_url, zipcode, openEI_api_end)
    response <- GET(openEI_url)
    # extract content and parse as JSON
    content <- content(response, "text")
    json <- fromJSON(content)

    # create a data frame with the extracted utility info
    utility_df <- data.frame(
      "zipcode" = rep(zipcode, each = nrow(json$items$label)),
      "label" = json$items$label,
      "utility" = json$items$utility,
      "rate_name" = json$items$name
    )

    # append the resulting data frame to the list
    utility_info[[length(utility_info) + 1]] <- utility_df
  }

  # combine the resulting data frames into a single data frame
  combined_utility_info <- do.call(rbind, utility_info)

  return(combined_utility_info)
}

utility_info_zips <- get_utility_data(zipcodes = zipcodes)

@@

```{r}
zipcodes <- c("46033", "93105", "90404")
## functiion wiith out for loop
get_zip_utility <- function(zipcode){
  openEI_start_url <- "https://api.openei.org/utility_rates?version=latest&format=json&sector=Residential&detail=full&approved=true&address="
openEI_api_end <- "&api_key=rU6MEqhK9OJ7obAnmcbzYhpFOenfBM5Q8GF0yJFA"
zipcode=zipcode

  openEI_url <- paste0(openEI_start_url, zipcode, openEI_api_end)
  response <- GET(openEI_url)
  # extract content and parse as JSON
  content <- content(EIresponse, "text")
  json <- fromJSON(content)

  utility_df <- data.frame(
  # repeat zipcode in each row for each utility observation
  "zipcode" = rep(zipcode, each=nrow(json$items$label)),
  "label" = json$items$label,
    "utility" = json$items$utility,
    "rate_name" = json$items$name)

}

test <- get_zip_utility("46033")
utility_info <- pmap(list(zipcode=zipcodes), get_zip_utility)

utilitu_info = as.data.frame(utility_info)
```
